Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-01-27 Thesis/chapter/060-results-material.tex
finish emma discusssion
captions for results pre-emma and emma

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \caption{SEM picture of \gls{zro} produces by H2O solution} \label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \caption{SEM picture of \gls{zro} produced by buoh solution} \label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
        \caption{115 fto cs 5x} \label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
        \caption{150 steel 2Fx5} \label{fig:sem-cs2}
    \end{subfigure}
	\caption{SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} \label{fig:sem}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{XRD}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra}
	\label{fig:xrd}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
        \caption{Transmission of \gls{zro} on glass} \label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
        \caption{Reflection of \gls{zro} on glass} \label{fig:ir-gr}
    \end{subfigure}
	\caption{\gls{uv}/\gls{vis}/\gls{nir}} Reflection vs Reflectance and Transmission vs Transmittance\label{fig:ir}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Current Voltage Curves} 
\begin{figure}
    \centering
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
        \caption{log good 3x4F} \label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
        \caption{log okay 10x1F} \label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
        \caption{log bad 3x3F} \label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
        \caption{stat good 3x4F} \label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
        \caption{stat okay 10x1F} \label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
        \caption{stat bad 3x3F} \label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
        \caption{no current} \label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
        \caption{diodic} \label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
        \caption{ohmic} \label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
    \caption{Current-voltage curves and the distribution of gradients for three representative samples, \td{include $\rho$ threshold}}  
    \label{fig:iv}
\end{figure}

>>>>

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
		\label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
		\label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
		\caption{}%115 fto cs 5x} 
		\label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
		\caption{}%150 steel 2Fx5} 
		\label{fig:sem-cs2}
    \end{subfigure}
	\caption{
		SEM images of of \gls{zro}:
		(a) \gls{zro} produces by aquatic solution on \gls{fto}
		(b) 10 layers of \gls{zro} on steel substrate
		(c) cross section of crack of 5 layers of \gls{zro} on fto 
		(d) side view of scratched \gls{zro} on steel substrate
		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
		\label{fig:sem}
	}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{XRD}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray}}
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
		\caption{}%Transmission of \gls{zro} on glass} 
		\label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
		\caption{}%Reflection of \gls{zro} on glass} 
		\label{fig:ir-gr}
    \end{subfigure}
	\label{fig:ir}
	\caption{UV/Vis/NIR spectra of different \gls{zro} layer counts on glass 
	(a)~transmission at \SI{0}{\degree} and (b)~reflection at \SI{45}{\degree} 
	} 
%	"138_g_00L_R.dpt"  w l t "0"  , \
%	"118_g_03L_R.dpt"  w l t "3"  , \
%	"114_g_05L_R.dpt"  w l t "5"  , \
%	"130_g_10L_R2.dpt" w l t "10" , \
%	"136_g_11L_R.dpt"  w l t "11"
%	Reflection vs Reflectance and Transmission vs Transmittance
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Current Voltage Curves} 
\begin{figure}
    \centering
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
		\caption{}%log good 3x4F} 
		\label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
		\caption{}%log okay 10x1F} 
		\label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
		\caption{}%log bad 3x3F} 
		\label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
		\caption{}%stat good 3x4F} 
		\label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
		\caption{}%stat okay 10x1F} 
		\label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
		\caption{}%stat bad 3x3F} 
		\label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
		\caption{}%no current} 
		\label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
		\caption{}%diodic} 
		\label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
		\caption{}%ohmic} 
		\label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
	\caption{
		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
		(a)-(c) I-V curves with log transformed current; 
		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
		(g)-(i) individual I-V measurements
	}
    \label{fig:iv}
\end{figure}

### 2023-01-27 Thesis/chapter/061-results-emma.tex
captions for results pre-emma and emma

\begin{table}[htb]
	\centering
    \caption{Global best per generation}
	\label{tab:emma-Gb}
	\begin{tabular}{ccccccccc}
        \hline\hline
		generation& measurements &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
        \hline
	1  &10	&1       &2    &4   &10   &40  &120  &300\\
	2  &15	&5       &2    &6   &10   &40  &120  &300\\
	3  &20	&2947    &4    &6   &16   &80 &1080  &300\\
	4  &25	&2405    &2    &6   &10   &40 &1080  &300\\
	5  &30	&13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\end{table}

\begin{table}
	\centering
    \caption{Predicted $\hat{\gamma}$} 
    \label{tab:emma-pred-G}
    \begin{tabular}{cccccc}
        \hline\hline
    enr &1st gen \gls{rf}   &2nd gen \gls{rf} &3rd gen \gls{rf}    &4th gen \gls{rf}   &5th gen \gls{rf}\\
        \hline
    1       &1.214185    &       &       &       &38.7962       \\
    5       &       &4.196626       &       &       &25.47335       \\
    2947    &       &       &10.9594    &       &10.9594       \\
    2405    &       &       &       &20.04962   &25.47335       \\
    13      &       &       &       &       &24.87178   \\
        \hline\hline
    \end{tabular}
\end{table}

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
The remaining input variables remained more or less the same except for the 3rd generation. 
\td{why?}
%
In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
except for sample 2947, which wasn't predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
%
Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
%The reason for is probably a 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).

@@

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d.}} 
    \label{fig:emma-gen}
\end{figure}

@@

\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
\td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
\url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
\fi

>>>>

\begin{table}[htb]
	\centering
    \caption{Global best per generation with experiment numbers and dependent variables/experiment conditions}
	\label{tab:emma-Gb}
	\begin{tabular}{ccccccccc}
        \hline\hline
		generation& measurements &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
        \hline
	1  &10	&1       &2    &4   &10   &40  &120  &300\\
	2  &15	&5       &2    &6   &10   &40  &120  &300\\
	3  &20	&2947    &4    &6   &16   &80 &1080  &300\\
	4  &25	&2405    &2    &6   &10   &40 &1080  &300\\
	5  &30	&13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\end{table}

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
The remaining input variables remained more or less the same except for the 3rd generation. 
\td{why?}
%
In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
except for sample 2947, which wasn't predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
\begin{table}
	\centering
    \caption{Predicted conductance measure $\hat{\gamma}$ for each generation by each generation's regression function}  
    \label{tab:emma-pred-G}
    \begin{tabular}{cccccc}
        \hline\hline
    enr &1st gen \gls{rf}   &2nd gen \gls{rf} &3rd gen \gls{rf}    &4th gen \gls{rf}   &5th gen \gls{rf}\\
        \hline
    1       &1.214185    &       &       &       &38.7962       \\
    5       &       &4.196626       &       &       &25.47335       \\
    2947    &       &       &10.9594    &       &10.9594       \\
    2405    &       &       &       &20.04962   &25.47335       \\
    13      &       &       &       &       &24.87178   \\
        \hline\hline
    \end{tabular}
\end{table}
%
Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
%The reason for is probably a 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).

@@

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{
		(a)~calculated conductance measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
		\td{describe more in-depth in text}
	}

    \label{fig:emma-gen}
\end{figure}

@@

\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
\td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
\url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
\fi
\td{TODO: find expression for $\gamma$: conductance measure, conducticity}
